---
title: "GSoC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GSoC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#devtools::install_github("ZeroDawn0D/tRiad")
library(tRiad)
```

# Introduction

This package has been developed as part of Google Summer of Code 2022, with the help of my mentors Di Cook and Harriet Mason. It calculates the Standard Delaunay Triangulations of a set of 2D points using the [Sloan(1987)](https://www.newcastle.edu.au/__data/assets/pdf_file/0017/22508/13_A-fast-algorithm-for-constructing-Delaunay-triangulations-in-the-plane.pdf) algorithm.

Link to GitHub repository: [ZeroDawn0D/tRiad](https://github.com/ZeroDawn0D/tRiad)

There are two ways to use triad:

## C++ functions (faster but harder to read and modify)

The `DelTri()` function creates an object of class `triad`. This object can be plotted.

```{r}
    x <- runif(100)
    y <- runif(100)
    o1 <- tRiad::DelTri(x,y)
    plot(o1, type = 'n')
```

## R functions (slower but easier to read and modify)

The `del.tri()` function does what `DelTri()` does. The object can be plotted in a similar way.

```{r}
x <- runif(10)
y <- runif(10)
o2 <- tRiad::del.tri(x,y)
plot(o2)

```

## Time comparisons

We also compare with `interp::tri.mesh()`

```{r}
#install.packages("interp")
library(interp)
x <- runif(500)
y <- runif(500)
```

```{r}
system.time(tRiad::del.tri(x,y))
```

```{r}
system.time(tRiad::DelTri(x,y))
```

```{r}
system.time(interp::tri.mesh(x,y))
```

For larger input:

```{r}
x <- runif(5000)
y <- runif(5000)
```

```{r}
system.time(tRiad::del.tri(x,y))
```

```{r}
system.time(tRiad::DelTri(x,y))
```

```{r}
system.time(interp::tri.mesh(x,y))
```

## SWAP subroutine

The code makes certain changes to the SWAP subroutine. For some reason, the algorithm as described in the paper broke when dealing with concave quadrilaterals.

```{r eval=FALSE}
swapR <- function(x1, y1, x2, y2, x3, y3, xp, yp){
  x1p <- x1 - xp
  y1p <- y1 - yp
  x2p <- x2 - xp
  y2p <- y2 - yp
  dot.1p.2p <- x1p*x2p + y1p*y2p
  mod1p <- sqrt(x1p*x1p + y1p*y1p)
  mod2p <- sqrt(x2p*x2p + y2p*y2p)
  cos.alpha <- dot.1p.2p / (mod1p * mod2p)
  if(cos.alpha > 1){
    cos.alpha <- 1
  }
  if(cos.alpha < -1){
    cos.alpha <- -1
  }
  alpha <- acos(cos.alpha)


  #angle between vector 3->1 and 3->2
  x13 <- x1 - x3
  y13 <- y1 - y3
  x23 <- x2 - x3
  y23 <- y2 - y3
  dot.13.23 <- x13*x23 + y13*y23
  mod13 <- sqrt(x13*x13 + y13*y13)
  mod23 <- sqrt(x23*x23 + y23*y23)
  cos.gamma <- dot.13.23/(mod13*mod23)
  if(cos.gamma > 1){
    cos.gamma <- 1
  }
  if(cos.gamma < -1){
    cos.gamma <- -1
  }
  gamma <- acos(cos.gamma)
  return((alpha+gamma) > pi)
}
```

## Further work

-   Implementing a C++ version of the Constrained Delaunay Triangulations. `tripack` has a FORTRAN implementation which is not open source
-   `plot.triad()` is slower than `plot.triSh()` although both are written in R. Optimise it even further
-   Optimise `DelTri()` to be as fast as `interp::tri.mesh()`, if not faster

## Optimising C++ code even further

The code makes use of `<vector.h>` and `<stack.h>` from the C++ Standard Template Library. Currently, I use `vector<vector<double>>` to represent 2D matrices, and ample use of `push_back()`. This leads to a lot of resizing that could slow down the code. I tried to reserve memory beforehand using `reserve()` but it became even slower. I also tried pre-allocating the memory but it did not work. There could be some way to use `double**` to optimise it. This is currently a work in progress.
